{\plant}: A package for modelling forest trait ecology \& evolution

### 2015-11-09 ms.tex
Change strategy name from FFW16 to FF16
With expansion of author list we needed to find something
easier to type than first initials of all authors.

Suggesting letters of first two authors and year of paper.

Matches changes in traitecoevo/plant#0a14be82b5d580f962398e3fa48a1111dd907279
Add author contribution statement

While we have implemented a particular physiological model
(\texttt{FF16}), the package is designed to allow arbitrary
additional physiologies to be introduced. Users are able to modify the
physiological model in two different ways. First, one can vary the
parameters of the \texttt{FF16} model directly (see Appendix
\ref{sec:FF16} for the list of parameters and Appendix \ref{sec:code} for code
examples). Second, we allow for changes in key parameters to bring
about changes in other parameters (a hyper-parameterisation), enabling the
straightforward modelling of trade-offs. For example, the
trait \textsc{lma} (leaf mass per unit leaf area) is used by default to estimate
the rate of leaf turnover ($k_l$), based on an observed scaling
relationship spanning across diverse vegetation and plant functional
types \citep{Wright-2004},
$$k_l = \beta_{kl1} \, \left(\phi / \phi_0\right)^{-\beta_{kl2}},$$
where $k_l$ and $\phi$ (\textsc{lma}) are both parameters of the core physiological
model, and $\beta_{kl1}, \beta_{kl2}, \phi_0$ are hyper-parameters. Such
linkages are defined within a user-supplied hyper-parameterisation function
(see Appendix \ref{sec:FF16} for details, or Appendix
\ref{sec:code} for code examples).
%
Finally, rather than varying the parameters of the existing equations
in the \texttt{FF16} model, the equations themselves can be
fundamentally changed. This requires defining a new physiological
model in a new C++ file and compiling that into the package. As an
example, in the \texttt{FFBDWdev} physiology, we have shown how to modify the
function determining allocation to reproduction.

@@

>>>>

While we have implemented a particular physiological model
(\texttt{FF16}), the package is designed to allow arbitrary
additional physiologies to be introduced. Users are able to modify the
physiological model in two different ways. First, one can vary the
parameters of the \texttt{FF16} model directly (see Appendix
\ref{sec:FF16} for the list of parameters and Appendix \ref{sec:code} for code
examples). Second, we allow for changes in key parameters to bring
about changes in other parameters (a hyper-parameterisation), enabling the
straightforward modelling of trade-offs. For example, the
trait \textsc{lma} (leaf mass per unit leaf area) is used by default to estimate
the rate of leaf turnover ($k_l$), based on an observed scaling
relationship spanning across diverse vegetation and plant functional
types \citep{Wright-2004},
$$k_l = \beta_{kl1} \, \left(\phi / \phi_0\right)^{-\beta_{kl2}},$$
where $k_l$ and $\phi$ (\textsc{lma}) are both parameters of the core physiological
model, and $\beta_{kl1}, \beta_{kl2}, \phi_0$ are hyper-parameters. Such
linkages are defined within a user-supplied hyper-parameterisation function
(see Appendix \ref{sec:FF16} for details, or Appendix
\ref{sec:code} for code examples).
%
Finally, rather than varying the parameters of the existing equations
in the \texttt{FF16} model, the equations themselves can be
fundamentally changed. This requires defining a new physiological
model in a new C++ file and compiling that into the package. As an
example, in the \texttt{FFdev} physiology, we have shown how to modify the
function determining allocation to reproduction.

@@

\section{Author contribution statement}

RGF and DSF wrote and developed the software, including numerical algorithms. AB and UD helped develop algorithms included in prototype software. DSF, RGF and MW wrote the the paper, with input from AB and UD. All authors contributed to material presented in Supplementary material.
